Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-04-07 Report/mse_formulation.tex
with_markku_corrections
updated - final - draft
antti-inputs

In this, we solve the \ac{JSFRA} problem by exploiting the equivalence between the \ac{MSE} and the achievable sum rate for the receivers designed based on the \ac{MMSE} criterion \cite{mse_duality,christensen2008weighted}. The \ac{MSE} \me{\epsilon_{l,k,n}}, for a data symbol \me{d_{l,k,n}} is given by
\iftoggle{single_column}{
\begin{multline} \label{mse-error}
	\mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise = \epsilon_{l,k,n}
\end{multline}
}{
\allowdisplaybreaks{
\begin{multline} \label{mse-error}
 \mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 \\
 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise = \epsilon_{l,k,n}
\end{multline}}
}
where \me{\hat{d}_{l,k,n}} is the estimate of the transmitted symbol. \review{Using the \ac{MMSE} receive beamformer \eqref{eqn-10} in the \ac{MSE} expression \eqref{mse-error} and in the \ac{SINR} expression \eqref{eq:SINR}, we can arrive at the following relation between the \ac{MSE} and the \ac{SINR} as}
\begin{equation} \label{eqn-mse-eq}
\epsilon_{l,k,n} = (1 + \gamma_{l,k,n})^{-1}.
\end{equation}
The above equivalence is valid only if the receivers are based on the \ac{MMSE} criterion. Using the equivalence in \eqref{eqn-mse-eq}, the \ac{WSRM} objective can be reformulated as the \ac{WMMSE} equivalent to obtain the precoders for the \acs{MU}-\acs{MIMO} scenario as discussed in \cite{christensen2008weighted,wmmse_shi,hong2012decomposition}. \review{Note that the receiver is invariably based on the \ac{MMSE} criterion irrespective of the \me{\ell_q} norm used in the objective function to obtain the optimal transmit precoders \me{\mvec{m}{l,k,n}}.}

Let \me{{v}^{\prime}_k = Q_k - \sum_{n=1}^N \sum_{l=1}^L t_{l,k,n}} denote the queue deviation corresponding to user \me{k} and \me{\tilde{{v}}^{\prime}_k \triangleq a_k^{1/{q}}v^{\prime}_k} represents the weighted equivalent. By using the relaxed \ac{MSE} expression in \eqref{mse-error}, the problem in \eqref{eqn-3} can be expressed as
\iftoggle{single_column}{
\begin{IEEEeqnarray}{rCl}\label{eqn-mse-1}
\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\ \epsilon_{l,k,n},\mvec{w}{l,k,n}}} {\text{minimize}} & \quad & \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-1.1} \\
\text{subject to} & \quad & t_{l,k,n} \leq -\log_2(\epsilon_{l,k,n}) \IEEEyessubnumber \label{eqn-mse-1.2} \\
 & \quad & \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise \eqspace \IEEEyessubnumber \label{eqn-mse-1.3} \\
& \quad \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \; \fall b. \IEEEyessubnumber  \eqspace \label{eqn-mse-1.4}
\end{IEEEeqnarray}
}{{\allowdisplaybreaks
\begin{IEEEeqnarray}{CL}\label{eqn-mse-1}
	\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\ \epsilon_{l,k,n},\mvec{w}{l,k,n}}} {\text{minimize}} & \quad \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-1.1} \\
	\text{subject to} & t_{l,k,n} \leq -\log_2(\epsilon_{l,k,n}) \IEEEyessubnumber \label{eqn-mse-1.2} \\
	& \sum_{{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise \nonumber \\	
	& \qquad + \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 \leq \epsilon_{l,k,n}\IEEEyessubnumber \label{eqn-mse-1.3} \\
	& \quad \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \; \fall b. \IEEEyessubnumber  \eqspace \label{eqn-mse-1.4}
\end{IEEEeqnarray}}}

>>>>

In this, we solve the \ac{JSFRA} problem by exploiting the equivalence between the \ac{MSE} and the achievable \ac{SINR} by using the receivers designed with the \ac{MMSE} criterion \cite{mse_duality,christensen2008weighted}. The \ac{MSE} \me{\epsilon_{l,k,n}}, for a data symbol \me{d_{l,k,n}} is given by
\iftoggle{single_column}{
\begin{multline} \label{mse-error}
	\mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise = \epsilon_{l,k,n}
\end{multline}}{\allowdisplaybreaks
\begin{multline} \label{mse-error}
 \mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 \\
 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise = \epsilon_{l,k,n}
\end{multline}}
where \me{\hat{d}_{l,k,n}} is the estimate of the transmitted symbol. \review{Using the \ac{MMSE} receive beamformer \eqref{eqn-10} in the \ac{MSE} expression \eqref{mse-error} and in the \ac{SINR} expression \eqref{eq:SINR}, we can arrive at the following relation between the \ac{MSE} and the \ac{SINR} as}
\begin{equation} \label{eqn-mse-eq}
\epsilon_{l,k,n} = (1 + \gamma_{l,k,n})^{-1}.
\end{equation}
The above equivalence is valid only if the receivers are based on the \ac{MMSE} criterion. Using the equivalence in \eqref{eqn-mse-eq}, the \ac{WSRM} objective can be reformulated as the \ac{WMMSE} equivalent to obtain the precoders for the \acs{MU}-\acs{MIMO} scenario as discussed in \cite{christensen2008weighted,wmmse_shi,hong2012decomposition}. \review{Note that the receiver is invariably based on the \ac{MMSE} criterion irrespective of the \me{\ell_q} norm used in the objective function to obtain the optimal transmit precoders \me{\mvec{m}{l,k,n}}.}

Let \me{{v}^{\prime}_k = Q_k - \sum_{n=1}^N \sum_{l=1}^L t_{l,k,n}} denote the queue deviation corresponding to user \me{k} and \me{\tilde{{v}}^{\prime}_k \triangleq a_k^{1/{q}}v^{\prime}_k} represents the weighted equivalent. By using the relaxed \ac{MSE} expression in \eqref{mse-error}, the problem in \eqref{eqn-3} can be expressed as
\iftoggle{single_column}{
\begin{IEEEeqnarray}{rCl}\label{eqn-mse-1}
\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\ \epsilon_{l,k,n},\mvec{w}{l,k,n}}} {\text{minimize}} & \quad & \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-1.1} \\
\text{subject to} & \quad & t_{l,k,n} \leq -\log_2(\epsilon_{l,k,n}) \IEEEyessubnumber \label{eqn-mse-1.2} \\
 & \quad & \epsilon_{l,k,n} \geq  \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise \eqspace \IEEEyessubnumber \label{eqn-mse-1.3} \\
& \quad \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \; \fall b. \IEEEyessubnumber  \eqspace \label{eqn-mse-1.4}
\end{IEEEeqnarray}
}{\allowdisplaybreaks
\begin{IEEEeqnarray}{CL}\label{eqn-mse-1}
	\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\\ \epsilon_{l,k,n},\mvec{w}{l,k,n}}} {\text{minimize}} & \quad \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-1.1} \\
	\text{subject to} & t_{l,k,n} \leq -\log_2(\epsilon_{l,k,n}) \IEEEyessubnumber \label{eqn-mse-1.2} \\
	& \sum_{{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise \nonumber \\	
	& \qquad + \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 \leq \epsilon_{l,k,n}\IEEEyessubnumber \label{eqn-mse-1.3} \\
	& \quad \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \sum_{l=1}^L \trace \, (\mvec{m}{l,k,n} \mvec{m}{l,k,n}^\herm) \leq P_{{\max}} \; \fall b. \IEEEyessubnumber  \eqspace \label{eqn-mse-1.4}
\end{IEEEeqnarray}}
